Deciding to Disclose

### 2017-01-16 Background.tex
Jakub1

Contrary to this, a meta-study by \citet{Gray2006} found there was
insufficient evidence to suggest any harm arising from moderate (under
1.5 UK units per day) alcohol consumption. This ties to the current
guidance from the \ac{NICE} \citep{NICE2010a}, advising that women
should avoid drinking at all in at least the first three months of
pregnancy, and no more than 1-2 units once or twice a week if they
do. In giving this advice, \ac{NICE} acknowledge that the risks to
the foetus from alcohol are a somewhat contentious subject, concluding
that the evidence of harm is inconclusive, but that this is not sufficient
to rule out the risk of negative outcomes. This tension is reflected
by earlier guidance from the \ac{RCOG} \citep{Gynecologists1996}
suggesting no evidence of harm below 15 units per week, and subsequent
criticism by \citet{Guerri1999}, who suggest that this might be interpreted
as legitimising \gls{binge}, while noting several studies indicating
adverse affects linked to even a single drink per day (e.g. \citet{Day1990}).
A subsequent \ac{RCOG} statement \citep{RoyalCollegeofObstetriciansandGynaecologists2006}
revised the recommendations to incorporate newer findings, advising
that there is no known safe threshold for drinking in pregnancy, and
highlighting binge drinking as of particular concern.

There has recently been an increased interest in the impact of binge
drinking, as a distinct pattern of consumption, with a wide variety
of negative outcomes reported by \citet{Maier2001}, although a significant
portion of their evidence base is drawn from animal studies which
augers for caution in generalising findings to humans. \citet{Strandberg-larsen2008}
explored links between binge drinking, and stillbirth, reporting a
statistically significant increase in risk associated with more than
three antenatal binge episodes. \citet{Sun2009} looked at seizure
disorders in children whose mothers binged during pregnancy. They
reported significantly greater risk of both neonatal seizures (\textasciitilde{}3
fold) and epilepsy (1.81 fold) associated with binge drinking between
11 and 16 weeks, but emphasised the exploratory nature of the results,
and need for replication. In terms of neurodevelopmental outcomes,
\citet{Streissguth1994} found a dose dependent association with scores
on timed word, and arithmetic tests in fourteen year olds with a stronger
association where bingeing occurred. A review by \citet{Henderson2007}
cautiously supports the contention that binge drinking has a neurodevelopmental
impact, but found no consistent support for adverse outcomes in pregnancy
(e.g. stillbirth, miscarriage, etc.) and note a paucity of studies
in the area. \citet{Meyer-Leu2011} considered the neonatal period,
finding that both moderate and binge drinking were associated with
an increased trend towards neonatal asphyxia. They also noted a large
number of contradictory findings and raising methodological concerns
about the studies reviewed by \citeauthor{Henderson2007}. \citet{Barr2006}
contend that binge drinking may also contribute to psychiatric issues
in the later life of offspring, although in this case their findings
are confined to individuals with \ac{FAS}, which may in itself be
a confounding factor, rather than indicating a directly causative
relationship between antenatal binge drinking and subsequent psychiatric
disorder in offspring.

@@

Stigma, or fear of a judgemental response on the part of the practitioner
should not however be taken uncritically to explain inaccurate reporting
by patients. While recent \ac{NICE} public health guidance advocates
routine alcohol misuse screening as a part of all practice \citep{NationalInstituteforHealthandCareExcellence2010},
there is no specific policy for routine antenatal care beyond providing
information on possible impacts of alcohol consumption \citep{NICE2010a}.
\ac{NICE} guidance on pregnancy and complex social factors \citep{NICE2010}
does specifically address women who misuse alcohol, but presupposes
knowledge of the problem through medical history, or via other services.
Taken in concert with the potential for harm from even moderate alcohol
use (section \ref{sub:Impact-of-Alcohol}), this suggests that much
of the onus is on the patient to volunteer information.

@@

In summation then, there is a consensus that alcohol consumption is
generally under reported in the pregnant population, with some support
for the idea that concern about social judgement associated with stigmatisation
may be a contributing factor. Of particular interest in the wider
context of this work, is the relationship between under reporting and
consumption, i.e. that heavier drinking is associated with a greater
tendency to understate intake.

\subsection{Practice Implications}

@@

In terms of the impact of continuity of care on health, rather than
experiential outcomes, research is relatively sparse. \citet{Marks2003}
examined the impact of continuity of care on \ac{PND}, which has
similar features to alcohol in that it carries an associated stigma
that can act as a barrier to help seeking \citep{Dennis2006}. Based
on the results of a \ac{RCT}, they conclude that continuity of care
is not protective, in the sense of reducing rates or impacting onset,
but was very successful in supporting engagement with treatment. Echoing
this, a 2009 Cochrane Review by \citet{Hatem2009} found no significant
difference in incidence of \ac{PND}, but reported benefits in terms
of lower rates of \gls{episiotomies}, anaesthesia, and shorter hospital
stays, with higher satisfaction as found by \citeauthor{Biro2003}.
While research in this area does not specifically pertain to disclosure,
the general trend in results are suggestive when taken in concert
with studies emphasising the importance of relationship building as
key in fostering a disclosure friendly environment. Continuity of
care is generally regarded as improving patient experience, and leading
to better health outcomes in the wider medical arena \citep{VanWalraven2010},
but is clearly not a cost free endeavour, with particular concern
arising from the emotional cost \citep{Todd1998}, and increased rates
of `\gls{burnout}' in practitioners \citep{Sandall1997}.

>>>>

Contrary to this, a meta-study by \citet{Gray2006} found there was
insufficient evidence to suggest any harm arising from moderate (under
1.5 UK units\footnote{10ml, or 8g of pure alcohol.} per day) alcohol consumption. This ties to the current
guidance from the \ac{NICE} \citep{NICE2010a}, advising that women
should avoid drinking at all in at least the first three months of
pregnancy, and no more than 1-2 units once or twice a week if they
do. In giving this advice, \ac{NICE} acknowledge that the risks to
the foetus from alcohol are a somewhat contentious subject, concluding
that the evidence of harm is inconclusive, but that this is not sufficient
to rule out the risk of negative outcomes. This tension is reflected
by earlier guidance from the \ac{RCOG} \citep{Gynecologists1996}
suggesting no evidence of harm below 15 units per week, and subsequent
criticism by \citet{Guerri1999}, who suggest that this might be interpreted
as legitimising \gls{binge}, while noting several studies indicating
adverse affects linked to even a single drink per day (e.g. \citet{Day1990}).
A subsequent \ac{RCOG} statement \citep{RoyalCollegeofObstetriciansandGynaecologists2006}
revised the recommendations to incorporate newer findings, advising
that there is no known safe threshold for drinking in pregnancy, and
highlighting binge drinking as of particular concern.

There has recently been an increased interest in the impact of binge
drinking, as a distinct pattern of consumption, with a wide variety
of negative outcomes reported by \citet{Maier2001}, although a significant
portion of their evidence base is drawn from animal studies which
augers for caution in generalising findings to humans. \citet{Strandberg-larsen2008}
explored links between binge drinking, and stillbirth, reporting a
statistically significant increase in risk associated with more than
three antenatal binge episodes. \citet{Sun2009} looked at seizure
disorders in children whose mothers binged during pregnancy. They
reported significantly greater risk of both neonatal seizures (ca. three-fold) and epilepsy (1.81-fold) associated with binge drinking between
11 and 16 weeks, but emphasised the exploratory nature of the results,
and need for replication. In terms of neurodevelopmental outcomes,
\citet{Streissguth1994} found a dose dependent association with scores
on timed word, and arithmetic tests in fourteen year olds with a stronger
association where bingeing occurred. A review by \citet{Henderson2007}
cautiously supports the contention that binge drinking has a neurodevelopmental
impact, but found no consistent support for adverse outcomes in pregnancy
(e.g. stillbirth, miscarriage, etc.) and note a paucity of studies
in the area. \citet{Meyer-Leu2011} considered the neonatal period,
finding that both moderate and binge drinking were associated with
an increased trend towards neonatal asphyxia. They also noted a large
number of contradictory findings and raising methodological concerns
about the studies reviewed by \citeauthor{Henderson2007}. \citet{Barr2006}
contend that binge drinking may also contribute to psychiatric issues
in the later life of offspring, although in this case their findings
are confined to individuals with \ac{FAS}, which may in itself be
a confounding factor, rather than indicating a directly causative
relationship between antenatal binge drinking and subsequent psychiatric
disorder in offspring.

@@

Stigma, or fear of a judgemental response on the part of the practitioner
should not however be taken uncritically to explain inaccurate reporting
by patients. While recent \ac{NICE} public health guidance advocates
routine alcohol misuse screening as a part of all practice,
there is no specific policy for routine antenatal care beyond providing
information on possible impacts of alcohol consumption \citep{NationalInstituteforHealthandCareExcellence2010,NICE2010a}.
\ac{NICE} guidance on pregnancy and complex social factors \citep{NICE2010}
does specifically address women who misuse alcohol, but presupposes
knowledge of the problem through medical history, or via other services.
Taken in concert with the potential for harm from even moderate alcohol
use (section \ref{sub:Impact-of-Alcohol}), this suggests that much
of the onus is on the patient to volunteer information.

@@

In summary then, there is a consensus that alcohol consumption is
generally under reported in the pregnant population, with some support
for the idea that concern about social judgement associated with stigmatisation
may be a contributing factor. Of particular interest in the wider
context of this work, is the relationship between under reporting and
consumption, i.e. that heavier drinking is associated with a greater
tendency to understate intake.

\subsection{Implications for Clinical Practice}

@@

In terms of the impact of continuity of care on health, rather than
experiential outcomes, research is relatively sparse. \citet{Marks2003}
examined the impact of continuity of care on \ac{PND}, which has
similar features to alcohol in that it carries an associated stigma
that can act as a barrier to help seeking \citep{Dennis2006}. Based
on the results of a \ac{RCT}, they conclude that continuity of care
is not protective, in the sense of reducing rates or impacting onset,
but was very successful in supporting engagement with treatment. Echoing
this, a 2009 Cochrane Review by \citet{Hatem2009} found no significant
difference in incidence of \ac{PND}, but reported benefits in terms
of lower rates of \gls{episiotomies}, anaesthesia, and shorter hospital
stays, with higher satisfaction as found by \citet{Biro2003}.
While research in this area does not specifically pertain to disclosure,
the general trend in results are suggestive when taken in concert
with studies emphasising the importance of relationship building as
key in fostering a disclosure friendly environment. Continuity of
care is generally regarded as improving patient experience, and leading
to better health outcomes in the wider medical arena \citep{VanWalraven2010},
but is clearly not a cost free endeavour, with particular concern
arising from the emotional cost \citep{Todd1998}, and increased rates
of `\gls{burnout}' in practitioners \citep{Sandall1997}.

### 2017-01-16 Introduction.tex
Jakub1

Turning more specifically to disclosure of alcohol use by women to healthcare professionals during their pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}. The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking. The simulation model described in this paper is able to replicate both qualitative trends, i.e. an increase in disclosure over appointments, and more honest behaviour by moderate as compared to heavier drinkers.

@@

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions. But equilibrium is the sine qua non of game theory, which is concerned with the stable outcome of an infinite contest of second guesses.
We wish to see the system in motion rather than just at rest, even if it does eventually settle to some stable point. Instead, we choose to focus on the behavioural processes driving a system in motion - a system \texit{out} of equilibrium - to understand how these processes interact with the movement.
Introducing decision theory takes a step down the ladder of abstraction from the mental chess of game theory. Dealing instead in the mechanics of decision making, and the calculus of choice, allows us to explore not only paths that arrive at the destinations we might consider in game theory, but also avenues not accessible where we constrain ourselves to a sometimes implausible degree of rationality.

@@

The remainder of this paper proceeds to review the substantive context of alcohol use and disclosure in the maternity context (section \ref{sec:alcohol_disclosure}), then outlines the proposed approach to model development (section \ref{sec:midwives_model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).

>>>>

Turning more specifically to disclosure of alcohol use by women to healthcare professionals during their pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}. The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post-partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking. The simulation model described in this paper is able to replicate both qualitative trends, i.e. an increase in disclosure over appointments, and more honest behaviour by moderate as compared to heavier drinkers.

@@

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions. But equilibrium is the \emph{sine qua non} of game theory, which is concerned with the stable outcome of an infinite contest of second guesses.
We wish to see the system in motion rather than just at rest, even if it does eventually settle to some stable point. Instead, we choose to focus on the behavioural processes driving a system in motion - a system \textit{out} of equilibrium - to understand how these processes interact with the movement.
Introducing decision theory takes a step down the ladder of abstraction from the mental chess of game theory. Dealing instead in the mechanics of decision making, and the calculus of choice, allows us to explore not only paths that arrive at the destinations we might consider in game theory, but also avenues not accessible where we constrain ourselves to a sometimes implausible degree of rationality.

@@

The remainder of this paper proceeds to review the substantive context of alcohol use and disclosure in the maternity context (section \ref{sec:alcohol_disclosure}), then outlines the proposed approach to model development (section \ref{sec:midwives_model}), and simulation experiments examining the abiility of the model to replicate qualitative trends in disclosure (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).

### 2017-01-16 Methods.tex
Tweaking figure placement
Spellchecking
Jakub1

This section provides details of experiments conducted to examine the ability of the model to reproduce qualitative trends reported in the midwifery literature by \citet{Alvik2006}, and \citet{Phillips2007}; as well as a global sensitivity analysis and construction of statistical emulators to explore, and contrast the response surfaces of the four decision rules.

@@

Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}). While there has been significant work on determining appropriate parametrisation for the model (e.g. \cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work. For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \acl{ALSPAC} suggest that the reality is far more positive\footnote{95.5\% of women in the sample reported consumption at, or below, \ac{NICE} recommended safe levels.} \citep{Humphriss2013}. The scenario was biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty. Payoffs were as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.

Two key measures were used: the fraction of the subpopulation who had ever signalled honestly, and the proportion of the population who were referred. Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.

\begin{table}[h!]
\caption{Model parameters.} 
\label{tab:qt_params}
\begin{tabular} {lll}
\hline\noalign{\smallskip}
Name & Description & Value \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(n_{w}\) & Number of women & 1000 \\ 
\(n_{m}\) & Number of midwives & 100 \\ 
\(r_{m}\) & Number of appointments per midwife & 1000 \\ 
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ 
Runs & Simulation runs & 1000 \\ 
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ 
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ 
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ 
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ 
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ 
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ 
\(q_{w}\) & Probability of women sharing & 0. \\ 
\(w_{w}\) & Weight of shared information for women & 0. \\ 
\(q_{m}\) & Probability of midwives sharing & 0. \\ 
\(w_{m}\) & Weight of shared information for midwives & 0. \\ 
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 10:1 \\ 
\(\gamma\) & Probability weighting for gains  & 0.61 \\ 
\(\delta\) & Probability weighting for losses &  0.69\\ 
\(\alpha\) & Power for gains  & 0.88 \\ 
\(\beta\) & Power for losses & 0.88 \\ 
\(\lambda\) & Loss aversion &  2.25 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple social learning within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends. The original experiment was repeated at \(q_{w},w_{w}\in \{0.25, 0.5, 0.75, 1 | q_{w}=w_{w}\}\), with 100 runs under each condition.

@@

In general, we have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques. For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}. This is a form of variance-based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs. The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem and then serves as an emulator for the simulator. The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propagates to uncertainty in the output, and how sharply the output responds to change in each parameter.

@@

@@

\begin{table}
\caption{Parameter ranges.}
\label{tab:sa_params}
\begin{tabular} {llll}
\hline\noalign{\smallskip}
Name & Description & Min & Max \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ 
\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ 
\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ 
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ 
\(q_{w}\) & Probability of women sharing & 0 & 1 \\ 
\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ 
\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ 
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ 
\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ 
\(x_{r}\) & Cost for referral & \multicolumn{2}{l}{\(-(x_{h} - 1)\)} \\ 
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1:1 & 100:1 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

>>>>

This section provides details of simulation experiments conducted to examine the ability of the model to reproduce qualitative trends reported in the midwifery literature by \citet{Alvik2006}, and \citet{Phillips2007}; as well as a global sensitivity analysis and construction of statistical emulators to explore, and contrast the response surfaces of the four decision rules.

@@

Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}). While there has been significant work on determining appropriate parameterisation for the model (e.g. \cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work. For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \acl{ALSPAC} suggest that the reality is far more positive\footnote{In this study 95.5\% of women in the sample reported consumption at, or below, \ac{NICE} recommended safe levels.} \citep{Humphriss2013}. The scenario was biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty. Payoffs were assumed as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.
\begin{table}[h!]
\caption[Midwives and women disclosure game model parameters]{Model parameters.} 
\label{tab:qt_params}
\begin{tabular} {lll}
\hline\noalign{\smallskip}
Name & Description & Value \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(n_{w}\) & Number of women & 1000 \\ 
\(n_{m}\) & Number of midwives & 100 \\ 
\(r_{m}\) & Number of appointments per midwife & 1000 \\ 
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ 
Runs & Simulation runs & 1000 \\ 
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ 
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ 
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ 
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ 
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ 
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ 
\(q_{w}\) & Probability of women sharing & 0. \\ 
\(w_{w}\) & Weight of shared information for women & 0. \\ 
\(q_{m}\) & Probability of midwives sharing & 0. \\ 
\(w_{m}\) & Weight of shared information for midwives & 0. \\ 
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 10:1 \\ 
\(\gamma\) & Probability weighting for gains  & 0.61 \\ 
\(\delta\) & Probability weighting for losses &  0.69\\ 
\(\alpha\) & Power for gains  & 0.88 \\ 
\(\beta\) & Power for losses & 0.88 \\ 
\(\lambda\) & Loss aversion &  2.25 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

Two key measures were used: the fraction of the subpopulation of women who had ever signalled honestly, and the proportion of the population who were referred for specialist treatment. Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.

In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple social learning within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends. The original experiment was repeated for different values of $q_{w}$ \(\{0.25, 0.5, 0.75, 1 | q_{w}=w_{w}\}\), with 100 runs under each condition.

@@

In general, we have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent-based models, although see \citet{Thiele2014} for a review of alternative techniques. For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}. This is a form of variance-based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs. The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem and then serves as an emulator for the simulator. The meta-model is then able to provide an indication about the extent to which uncertainty in a parameter propagates to uncertainty in the output, and how sharply the output responds to change in each parameter.

@@

\begin{table}
\caption[Parameter ranges for sensitivity analysis of the midwives and women disclosure game model]{Parameter ranges.}
\label{tab:sa_params}
\begin{tabular} {llll}
\hline\noalign{\smallskip}
Name & Description & Min & Max \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ 
\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ 
\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ 
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ 
\(q_{w}\) & Probability of women sharing & 0 & 1 \\ 
\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ 
\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ 
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ 
\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ 
\(x_{r}\) & Cost for referral & \multicolumn{2}{l}{\(-(x_{h} - 1)\)} \\ 
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1:1 & 100:1 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

@@

### 2017-01-16 Model.tex
Jakub1

In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals. We also impose a discretisation on the continuum of alcohol use, and use three types of behaviour - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy. Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.

Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental. The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response, which is to either refer the woman for specialist treatment, or do nothing.

@@

\begin{table}
\centering
\caption{Payoff matrices}
\label{tab:Payoff-matrix}
\begin{subtable}[]{\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline
\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Harsh & -2 & -1 & 0\tabularnewline
\cline{2-5} 
 & Moderate & -1 & 0 & 0\tabularnewline
\cline{2-5} 
 & Non & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}
\caption{Social cost, \(X_{s}\), for women, given their signal, and the midwife's type}
\label{tab:Social-cost-matrix}

\end{subtable}
\begin{subtable}[]{\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & 10 & 10 & 10\tabularnewline
\cline{2-5} 
 & Don't refer & -2 & -1 & 10\tabularnewline
\hline 
\end{tabular}
\caption{Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type}
\label{tab:Referral-payoff-matrix}
\end{subtable}
\begin{subtable}[]{\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9 & -9 & -9 \tabularnewline
\cline{2-5} 
 & Don't refer & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}
\caption{Referral cost, \(X_{c}\), for midwife, given their action and the woman's type}
\label{tab:inst_cost_matrix}
\end{subtable}
\end{table}

@@

As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)). They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them. If they are not referred, they rejoin the back of the queue after their appointment. In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.

@@

Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently. The simple payoff based rule relies on a belief structure relating actions directly to rewards which is essentially model free. Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario. As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.

A payoff based agent, who is a light drinker, hears the account of the heavy drinker. They take the account as literally happening to them, and update their beliefs to include the possibility that there is a negative outcome attached to claiming to be a light drinker.

>>>>

In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals. We also impose a discretisation on the continuum of alcohol use, and use three types of behaviour --- light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy. Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.

Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern --- non-judgemental, moderately judgemental, and harshly judgemental. The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response, which is to either refer the woman for specialist treatment, or do nothing.

@@

\begin{table}
\centering%!
\caption[Payoff matrices for midwives, and women in the disclosure game]{Payoff matrices}
\label{tab:Payoff-matrix}
\begin{subtable}[]{\textwidth}\centering%!
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline
\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Harsh & -2 & -1 & 0\tabularnewline
\cline{2-5} 
 & Moderate & -1 & 0 & 0\tabularnewline
\cline{2-5} 
 & Nonjudgemental & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}
\caption{Social cost, \(X_{s}\), for women, given their signal, and the midwife's type}
\label{tab:Social-cost-matrix}

\end{subtable}
\begin{subtable}[]{\textwidth}\centering%!
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & 10 & 10 & 10\tabularnewline
\cline{2-5} 
 & Don't refer & -2 & -1 & 10\tabularnewline
\hline 
\end{tabular}
\caption{Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type}
\label{tab:Referral-payoff-matrix}
\end{subtable}
\begin{subtable}[]{\textwidth}\centering%!
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9 & -9 & -9 \tabularnewline
\cline{2-5} 
 & Don't refer & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}
\caption{Referral cost, \(X_{c}\), for midwife, given their action and the woman's type}
\label{tab:inst_cost_matrix}
\end{subtable}\par% !
\end{table}

@@

As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)). They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred for specialist treatment, and a new player is drawn from the same distribution that produced the original players to replace them. If they are not referred, they rejoin the back of the queue after their appointment. In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.

@@

Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently. The simple payoff-based rule relies on a belief structure relating actions directly to rewards which is essentially model free. Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario. As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.

A payoff-based agent, who is a light drinker, hears the account of the heavy drinker. They take the account as literally happening to them, and update their beliefs to include the possibility that there is a negative outcome attached to claiming to be a light drinker.
